---
title: "RF_Demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## I. RF result

### I.1 Final features, Confusion matrix, Recall, ACC, and AUC

```{r}
names(df_RF6)
result6
print(rf.strata6)
```

### I.2 Feature Importance Plot

```{r}
as.data.frame(rf.strata6$importance) %>% arrange(MeanDecreaseAccuracy)
varImpPlot(rf.strata6)
```

### I.3 Prob output of testing data

```{r}
View(result)
```



## II. RF classification cutoff/threshold

### II.1 Prob hist: x-axis is prob_F

```{r}
fig1
```

### II.2 TPR vs FPR curve: find a vertical line that max TPR and min FPR

```{r}
fig2
```

### II.3 ROC curve:trade-off between sensitivity (or TPR) and specificity (1 – FPR)

```{r}
fig_roc
```

### II.4 PR curve: Precision(TP/pred P) vs Recall(TP/actual P)
Higher threshold will increase recall much but only slightly decrease precision
```{r}
fig_pr
```

### II.5 New cutoff: Confusion matrix before vs after
result_new['prob_F']<0.55=T(give more T)
```{r}
table(result_new['actual'][[1]], result_new['pred_new'][[1]])
table(result['actual'][[1]], result['pred'][[1]])
```


## III. RF interpretation

### III.1 PDP plot: yhat=prob_F
How different values of 1 interested feature changes prob_F
```{r}
plot.pdp #diff_week_mean: nonlinear
plot.pdp1 #with_web: no web=F, with web=T
plot.pdp2 #FB_Page_Follows: more follows=T
plot.pdp3 #Avg_Rating_mean: nonlinear,high rating=T
plot.pdp4 #State_G: high group(3)=T
```

### III.2 Prob_T Decomposition

```{r}
View(result_feature)

#Most frequent deterministic feature
#diff_week_mean>State_G>Avg_Rating_mean>FB_Page_Follows>with_web
f1
f2
f3

#Positive vs Negative contribution
summary(result_feature$diff_week_mean) #negative contribution dominates
summary(result_feature$State_G) #balanced contribution
summary(result_feature$Avg_Rating_mean) #balanced contribution
summary(result_feature$FB_Page_Follows) #negative contribution dominates
summary(result_feature$with_web) #balanced contribution
```

### III.3 SHAP & Error Analysis

```{r}
View(result_FN)
View(result_FP)
```

#### Check Top5 FN error individual 
```{r}
#704:all negative, but convert(have profile in many platform but no data, reviews 10 years ago)
error_index<-704
shap_individual(error_index)  
#View(df_shap_all[sample==F,][error_index,])
#View(df_shap_sim[sample==F,][error_index,])
error_id<-df_shap_all[sample==F,][error_index,'Id'][[1]]
#View(df_raw[df_raw['Id']==error_id,])
              
#496:have profile in many platform but no data, new reviews 7/20
error_index<-496
shap_individual(error_index)  
#View(df_shap_all[sample==F,][error_index,])
#View(df_shap_sim[sample==F,][error_index,])
error_id<-df_shap_all[sample==F,][error_index,'Id'][[1]]
#View(df_raw[df_raw['Id']==error_id,])

#837/848:HA only, no data
error_index<-837
shap_individual(error_index)  
#View(df_shap_all[sample==F,][error_index,])
#View(df_shap_sim[sample==F,][error_index,])
error_id<-df_shap_all[sample==F,][error_index,'Id'][[1]]
#View(df_raw[df_raw['Id']==error_id,])

#595:only HA(1 review), no web, low state(Minneapolis)
error_index<-595
shap_individual(error_index)  
#View(df_shap_all[sample==F,][error_index,])
#View(df_shap_sim[sample==F,][error_index,])
error_id<-df_shap_all[sample==F,][error_index,'Id'][[1]]
#View(df_raw[df_raw['Id']==error_id,])
```

#### Check FP error individual
```{r}
#184:HA/Google, mid size good review, active
error_index<-184
shap_individual(error_index)  
#View(df_shap_all[sample==F,][error_index,])
#View(df_shap_sim[sample==F,][error_index,])
error_id<-df_shap_all[sample==F,][error_index,'Id'][[1]]
#View(df_raw[df_raw['Id']==error_id,])
```


## IV. Random Other Info

### IV.1 Correlation Heatmap

```{r}
ggcorrplot::ggcorrplot(cor(df_RF6 %>% select(-Conversion)))
```

### II.2 PCA: only 2PC in plot

```{r}
fig
prin_comp
summary(prin_comp)
```

