---
title: "EDA_Demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source('EDA.R')
```
## O. Conversion across platform
1Yelp or 2Yelp means High Conversion, not included 3Yelp
More cateogries or regroup for Profile existence may lead higher prediction power? 
```{r}
df_P1
```
```{r}
#Adding Google Profile does not change previous patterns
cn1<-sum(df_G$Conversion)/nrow(df_G) #0.0731
df_G %>% group_by(Angi_P,HA_P,Yelp_P,Google_P) %>%
  summarise(n = n(), c=sum(Conversion)) %>% mutate(pc=round(c/n*100,2), all=round(cn1*100,2)) %>% 
  arrange(desc(pc))
```


## I. Occupation vs Conversion rate: How to group Occupation?
### I.1 By conversion rate
```{r}
df_oc
```

### I.2 By platform
Angi's High Conversion Occupation Group Top 6: 'Inspector and Restorer','Pest Control Specialist','Carpenter','Roofer and Sider','	Locksmith','Cleaner'

HA&Yelp's High Conversion Occupation Group Top 6: 'Inspector and Restorer','Pest Control Specialist', 'Furniture Service Specialist','Cleaner','Floor, Carpet, and Tile Specialist','Landscaper'
```{r}
df_occu_P
```

### I.3 By Number of Reviews

### I.3.0 Put together all 'High Number of Reviews Occupation' identified
```{r}
Angi_name_R<-Angi_reoccu_R2[1:6,'occupation'][[1]]
HA_name_R<-HA_reoccu_R2[1:8,'occupation'][[1]]
Yelp_name_R<-Yelp_reoccu_R2[1:10,'occupation'][[1]]
G_name_R<-G_reoccu_R2[1:10,'occupation'][[1]]

table(c(Angi_name_R,HA_name_R,Yelp_name_R,G_name_R))
```

### I.3.1 Angi
Not significant, small sample size, High Review Occupation Group=Higher Conversion rate
```{r}
summary(with_Angi$Angi_s___of_Reviews) #6
Angi_reoccu_R2
Angi_reoccu_R2[1:6,'occupation'][[1]]
Angi_reoccu_R2_f
```

```{r}
summary(lm(with_Angi$Conversion~with_Angi$Angi_s___of_Reviews)) #not sig
#summary(lm(with_Angi$Conversion~with_Angi$occu_group)) #not sig, smaller p value, larger R^2

Angi_reoccu_R2_h<-with_Angi %>% filter(occu_group=='High') %>% select(Angi_s___of_Reviews,Conversion)
summary(lm(Angi_reoccu_R2_h$Conversion~Angi_reoccu_R2_h$Angi_s___of_Reviews)) #not sig, smaller p value
Angi_reoccu_R2_l<-with_Angi %>% filter(occu_group=='Low') %>% select(Angi_s___of_Reviews,Conversion)
summary(lm(Angi_reoccu_R2_l$Conversion~Angi_reoccu_R2_l$Angi_s___of_Reviews)) #not sig, larger p value
```

### I.3.2 HA
Significant, High Review Occupation Group=Higher Conversion rate
```{r}
summary(with_HA$HA___of_Reviews) #2
HA_reoccu_R2
HA_reoccu_R2[1:8,'occupation'][[1]]
HA_reoccu_R2_f
```

```{r}
summary(lm(with_HA$Conversion~with_HA$HA___of_Reviews)) #sig

HA_reoccu_R2_h<-with_HA %>% filter(occu_group=='High') %>% select(HA___of_Reviews,Conversion)
summary(lm(HA_reoccu_R2_h$Conversion~HA_reoccu_R2_h$HA___of_Reviews)) #more sig
HA_reoccu_R2_l<-with_HA %>% filter(occu_group=='Low') %>% select(HA___of_Reviews,Conversion)
summary(lm(HA_reoccu_R2_l$Conversion~HA_reoccu_R2_l$HA___of_Reviews)) #not sig
```

### I.3.3 Yelp
Slightly Sig after grouping, sample size? Different patterns in different occupation group
```{r}
summary(with_Yelp$Yelp___of_Reviews) #1
Yelp_reoccu_R2
Yelp_reoccu_R2[1:10,'occupation'][[1]]
Yelp_reoccu_R2_f
```

```{r}
summary(lm(with_Yelp$Conversion~with_Yelp$Yelp___of_Reviews)) #not sig overall

Yelp_reoccu_R2_h<-with_Yelp %>% filter(occu_group=='High') %>% select(Yelp___of_Reviews,Conversion)
summary(lm(Yelp_reoccu_R2_h$Conversion~Yelp_reoccu_R2_h$Yelp___of_Reviews)) #not sig, larger p value
Yelp_reoccu_R2_l<-with_Yelp %>% filter(occu_group=='Low') %>% select(Yelp___of_Reviews,Conversion)
summary(lm(Yelp_reoccu_R2_l$Conversion~Yelp_reoccu_R2_l$Yelp___of_Reviews)) #slightly sig, smaller p value
```

### I.3.4 Google
Not Significant, High Review Occupation Group=Higher Conversion rate
```{r}
summary(with_G$Google___of_Reviews) #4
G_reoccu_R2
G_reoccu_R2[1:10,'occupation'][[1]]
G_reoccu_R2_f
```

```{r}
summary(lm(with_G$Conversion~with_G$Google___of_Reviews)) #not sig overall

G_reoccu_R2_h<-with_G %>% filter(occu_group=='High') %>% select(Google___of_Reviews,Conversion)
summary(lm(G_reoccu_R2_h$Conversion~G_reoccu_R2_h$Google___of_Reviews)) #not sig, smaller p value
G_reoccu_R2_l<-with_G %>% filter(occu_group=='Low') %>% select(Google___of_Reviews,Conversion)
summary(lm(G_reoccu_R2_l$Conversion~G_reoccu_R2_l$Google___of_Reviews)) #not sig, larger p value
```

### I.4 By Avg Ratings

### I.4.0 Put together all 'High Rating Occupation' identified
```{r}
Angi_name_RA<-Angi_reoccu_RA2[1:10,'occupation'][[1]]
HA_name_RA<-HA_reoccu_RA2[1:8,'occupation'][[1]]
Yelp_name_RA<-Yelp_reoccu_RA2[1:5,'occupation'][[1]]
G_name_RA<-G_reoccu_RA2[1:11,'occupation'][[1]]

table(c(Angi_name_RA,HA_name_RA,Yelp_name_RA,G_name_RA))
```

### I.4.1 Angi
Not Sig, Ratings are too close to generate occupation groups
```{r}
summary(Angi_RA$Angi_s_Avg_Rating) #4.9
Angi_reoccu_RA2
Angi_reoccu_RA2[1:10,'occupation'][[1]]
Angi_reoccu_RA2_f
summary(lm(Angi_RA$Conversion~Angi_RA$Angi_s_Avg_Rating))
```

### I.4.2 HA
Significant, Ratings are too close to generate occupation groups
```{r}
summary(HA_RA$HA_Avg_Rating) #4.9
HA_reoccu_RA2
summary(lm(HA_RA$Conversion~HA_RA$HA_Avg_Rating))
```

### I.4.3 Yelp
Sig, sample size issue when grouping?
```{r}
summary(Yelp_RA$Yelp_Avg_Rating) #4.5
Yelp_reoccu_RA2
summary(lm(Yelp_RA$Conversion~Yelp_RA$Yelp_Avg_Rating))
```

### I.4.4 Google
Sig, but occupation group make it less sig, High Rating=High conversion rate
```{r}
summary(G_RA$Google_Avg_Rating) #4.9
G_reoccu_RA2
G_reoccu_RA2[1:11,'occupation'][[1]]
G_reoccu_RA2_f
```

```{r}
summary(lm(G_RA$Conversion~G_RA$Google_Avg_Rating))
```

## II. Number of Reviews vs Conversion rate:
Angi:
more reviews=more convert
number of reviews has no sig in Angi, lower power after grouping
```{r}
Angi_R
Angi_rew_group
summary(lm(with_Angi$Conversion~with_Angi$rew_group))
summary(lm(with_Angi$Conversion~with_Angi$Angi_s___of_Reviews))
#View(with_Angi[which(with_Angi$Angi_s___of_Reviews>500),]) #Top 7 are HVAC Specialist, 3 Plumber
```

more reviews=more convert
Higher power after grouping
```{r}
HA_R
HA_rew_group
summary(lm(with_HA$Conversion~with_HA$rew_group))
summary(lm(with_HA$Conversion~with_HA$HA___of_Reviews))
```

```{r}
Yelp_R
Yelp_rew_group
summary(lm(with_Yelp$Conversion~with_Yelp$rew_group))
summary(lm(with_Yelp$Conversion~with_Yelp$Yelp___of_Reviews))
```

